Results

### 2025-09-29 notebooks/00_index.qmd
feat: plotting figures

import PSPAnisotropy.Labels as 𝑳
import PSPAnisotropy.YLabel as 𝒀

@@

using Unitful
Unitful.preferunits(u"nA", u"km")
unitify(u) = (*)$u
unitify(u::String) = (*)$uparse(u)
```

@@

```{julia}
df, configs = workload()
compute_params!(df)
compute_Alfvenicity_params!(df)

psp_df = @rsubset(df, :id == "PSP"; view=true)
psp_config = configs[1]
wind_df = @rsubset(df, :id == "Wind"; view=true)
wind_config = configs[2]
thm_df = @rsubset(df, :id == "THEMIS"; view=true)
thm_config = configs[3]

thm_config["B"] = unitify("nT") ∘ thm_config["B"]
```

```{julia}
using DimensionalData

deunit(x::Quantity, u) = NoUnits(x / u)
deunit(x, u) = x

function add_temp_anisotropy!(df, Tp_para, Tp_perp, Te_para, Te_perp, dt=Minute(1))
    @rtransform! df begin
        :Tp_para = deunit(tselect(Tp_para, :time, dt), u"eV")
        :Tp_perp = deunit(tselect(Tp_perp, :time, dt), u"eV")
        :Te_para = deunit(tselect(Te_para, :time, dt), u"eV")
        :Te_perp = deunit(tselect(Te_perp, :time, dt), u"eV")
    end
end

add_temp_anisotropy!(df, Tp, Te, args...) =
    add_temp_anisotropy!(df, Tp.para, Tp.perp, Te.para, Te.perp, args...)

function compute_PSP_anisotropy_params!(psp_df)
    Tp = PSP.read_proton_temperature(7:8)
    Te = PSP.read_electron_temperature()
    add_temp_anisotropy!(psp_df, Tp, Te)
    compute_anisotropy_params!(psp_df, :ion => (:Tp_para, :Tp_perp), :electron => (:Te_para, :Te_perp))
end

function compute_Wind_anisotropy_params!(df, tmin, tmax)
    Wind_Tp2 = Wind.pTemp_T2(tmin, tmax; add_unit=false)
    Wind_Te2 = Wind.eTemp_T2(tmin, tmax; add_unit=false)
    add_temp_anisotropy!(df, Wind_Tp2, Wind_Te2, Minute(2))
    compute_anisotropy_params!(df, :ion => (:Tp_para, :Tp_perp), :electron => (:Te_para, :Te_perp))
end
```

```{julia}
f = Figure(; size=(1200, 800))
psp_event = filter_low_mva_quality(psp_df)[5, :]
fax, res_psp = plot_candidate(f[1, 1], psp_event, psp_config, Second(10))
@info "v_l_ratio" psp_event.V_l_ratio psp_event.V_l_ratio_max
# res_thm = plot_candidate(f[1, 2], thm_df[10, :], thm_config)
# res_thm = plot_candidate(f[1, 2], thm_df[14, :], thm_config)
# res_thm = plot_candidate(f[1, 2], thm_df[17, :], thm_config)
# res_wind = plot_candidate(f[1, 3], wind_df[1, :], wind_config, Second(10))
f
```

@@

```{julia}
using Speasy
using SPEDAS: tnorm_combine, tplot, DataSet
using DimensionalData
using CairoMakie
# using GLMakie
using Statistics
using PartialFunctions
using Unitful
using SPEDAS.SpaceDataModel: set, extend, @set

@@

```{julia}
tmin_psp = DateTime("2021-01-14")
tmax_psp = DateTime("2021-01-20")
tmin_wind = DateTime("2021-01-15")
tmax_wind = DateTime("2021-01-23")
_tmax_wind = DateTime("2021-01-15T02")

tmin_psp = DateTime("2021-01-16")
tmax_psp = DateTime("2021-01-19")
# tmin_wind = DateTime("2021-01-17")
# tmax_wind = DateTime("2021-01-18")
```

@@

```{julia}
function modify_faxs_base!(faxs)
    B_ax = faxs.axes[1]
    B_ax.ylabel[] = 𝒀.B
    V_ax = faxs.axes[3]
    V_ax.ylabel[] = 𝒀.V
    n_ax = faxs.axes[2]
    n_ax.yscale[] = identity
    n_ax.ylabel[] = 𝒀.n
end

function modify_faxs_vl!(faxs)
    i = 1
    T_ax = faxs.axes[end-3-i]
    T_ax.ylabel[] = "T (eV)"

    R_ax = faxs.axes[end-2-i]
    ylims!(R_ax, 0.09, 0.85)

    β_ax = faxs.axes[end-i]
    β_ax.yscale[] = log10
    ylims!(β_ax, 8e-2, 4e1)

    A_He_ax = faxs.axes[end]
    A_He_ax.yscale[] = identity
    A_He_ax.ylabel[] = L"A_{\text{He}} (%)"
    ylims!(A_He_ax, 0, 8)
end

f = Figure(; size=(800, 600))
# faxs = plot_PSP(f[1, 1], tmin_psp, tmax_psp, get_vl_ratio_ts(psp_df)...)
modify_faxs_vl!(faxs)
f
```

```{julia}
let tmin = tmin_psp, tmax = tmax_psp
    f = Figure(; size=(800, 600))

    faxs = plot_Wind(f[1, 1], tmin_psp, tmax_psp, get_vl_ratio_ts(wind_df)...)
    f
end
```

```{julia}
using SPEDAS: tvec
using CairoMakie
CairoMakie.activate!()

@@

# for enc in 7:9
plot_vl_ratio = true

for enc in 7:7
    (tmin_psp, tmax_psp), (tmin_wind, tmax_wind) = get_timerange(enc)

    legend = (; position=Top())
    labels = '1':'9'
    padding = (0, 30, 0, -30)

    f = Figure(; size=(800, 600))

    fname = "overview-$enc"

    if plot_vl_ratio
        fname = "overview-vl-$enc"
        faxs = plot_PSP(f[1, 1], tmin_psp, tmax_psp, get_vl_ratio_ts(psp_df)...; legend)
        modify_faxs_base!(faxs)
        plot_vl_ratio && modify_faxs_vl!(faxs)

        compute_Wind_anisotropy_params!(wind_df, tmin_wind, tmax_wind)
        faxs = plot_Wind(f[1, 2], tmin_wind, tmax_wind, get_vl_ratio_ts(wind_df)...; legend)
        modify_faxs_base!(faxs)
        plot_vl_ratio && modify_faxs_vl!(faxs)
    end

    add_labels!(f[1, 1]; labels, open="(a.", padding)
    add_labels!(f[1, 2]; labels, open="(b.", padding)

    easy_save(fname; formats=(:pdf,))
    display(f)

    # tvars_psp = (psp_B, psp_n, psp_V)
    # tvars_wind = (wind_B, wind_n, wind_V)
    # f = Figure(; size=(1200, 600))
    # plots = tplot(f[1, 1], tvars_psp, tmin_psp, tmax_psp; legend)
    # add_labels!(f[1, 1]; labels, open="(a.")
    # tplot(f[1, 2], tvars_wind, tmin_wind, tmax_wind; legend)
    # add_labels!(f[1, 2]; labels, open="(b.")
    # tplot(f[1, 3], _tmask! .∘ tvars_themis, tmin_wind, tmax_wind; legend)
    # add_labels!(f[1, 3]; labels, open="(c.")
    # easy_save("overview-$enc-all")
end
```

@@

```{julia}
psp_df_taus = map([2, 4, 8, 16, 32]) do tau
    psp_config["tau"] = tau
    df = PSPAnisotropy.produce(psp_config, psp_config["timeranges"][1]...)
    @transform! df :tau = tau
    compute_Alfvenicity_params!(df)
end

wind_df_taus = map([2, 4, 8, 16, 32]) do tau
    wind_config["tau"] = tau
    df = PSPAnisotropy.produce(wind_config, wind_config["timeranges"][1]...)
    @transform! df :tau = tau
    compute_Alfvenicity_params!(df)
end
```

@@

```{julia}
f = Figure(; size=(1200, 800))
# let df = psp_df_taus[1], config = psp_config
begin
    df = @subset(wind_df_taus[1], :index_std .> 4)
    config = wind_config
    event = filter_low_mva_quality(df)[5, :]
    fax, res_psp = plot_candidate(f[1, 1], event, config, Second(10))
    plot_var_info!(fax, event)
    @info "v_l_ratio" event.V_l_ratio event.V_l_ratio_max
end
f
```

@@

# AoG fix
using LaTeXStrings
import AlgebraOfGraphics: append_unit_string
append_unit_string(s::LaTeXStrings.LaTeXString, u::String) = s

function alpha_layer(df, alpha)
    psp_df = @rsubset(df, :id == "PSP"; view=true)
    thm_df = @rsubset(df, :id == "THEMIS"; view=true)
    wind_df = @rsubset(df, :id == "Wind"; view=true)
    (data(thm_df) + data(wind_df)) * visual(; alpha) + data(psp_df)
end
```

>>>>

@@

using Unitful
Unitful.preferunits(u"nA", u"km")
unitify(u) = (*)$u
unitify(u::String) = (*)$uparse(u)
includet("../src/plot.jl")
```

```{julia}
df = workload()
compute_params!(df)
compute_Alfvenicity_params!(df)

psp_df = @rsubset(df, :id == "PSP"; view=true)
wind_df = @rsubset(df, :id == "Wind"; view=true)
thm_df = @rsubset(df, :id == "THEMIS"; view=true)p -
         thm_conf["B"] = unitify("nT") ∘ thm_conf["B"]
```

```{julia}
compute_PSP_anisotropy_params!(psp_df)
for enc in 7:9
    (tmin_psp, tmax_psp), (tmin_wind, tmax_wind) = get_timerange(enc)
    wind_df_enc = @rsubset(wind_df, :enc == enc; view=true)
    compute_Wind_anisotropy_params!(wind_df_enc, tmin_wind, tmax_wind)
end
```

@@

```{julia}
f = Figure(; size=(1200, 800))
psp_event = filter_low_mva_quality(psp_df)[5, :]
fax, res_psp = plot_candidate(f[1, 1], psp_event, psp_conf, Second(10))
@info "v_l_ratio" psp_event.V_l_ratio psp_event.V_l_ratio_max
# res_thm = plot_candidate(f[1, 2], thm_df[10, :], thm_conf)
# res_thm = plot_candidate(f[1, 2], thm_df[14, :], thm_conf)
# res_thm = plot_candidate(f[1, 2], thm_df[17, :], thm_conf)
# res_wind = plot_candidate(f[1, 3], wind_df[1, :], wind_conf, Second(10))
f
```

@@

```{julia}
using Speasy
using SPEDAS: tnorm_combine, DataSet
using DimensionalData
# using CairoMakie
using GLMakie
using Statistics
using PartialFunctions
using Unitful
using SPEDAS.SpaceDataModel: set, extend, @set

@@

```{julia}
tmin_psp = DateTime("2021-01-15")
tmax_psp = DateTime("2021-01-20")
tmin_wind = DateTime("2021-01-17")
tmax_wind = DateTime("2021-01-23")
_tmax_wind = DateTime("2021-01-15T02")

# tmin_psp = DateTime("2021-01-16")
# tmax_psp = DateTime("2021-01-19")
# tmin_wind = DateTime("2021-01-17")
# tmax_wind = DateTime("2021-01-18")
```

@@

```{julia}
f = Figure(; size=(800, 600))
faxs = plot_PSP(f[1, 1], tmin_psp + Day(2), tmin_psp + Day(3), get_vl_ratio_ts(psp_df)...)
modify_faxs_base!(faxs)
# modify_faxs_vl!(faxs)
f
```

```{julia}
let tmin = tmin_wind, tmax = tmin_wind + Day(3)
    f = Figure(; size=(800, 600))
    faxs = plot_Wind(f[1, 1], tmin, tmax, get_vl_ratio_ts(wind_df)...)
    modify_faxs_base!(faxs)
    f
end
```

```{julia}
# using CairoMakie
# CairoMakie.activate!()

@@

add_vl_ratio = true

for enc in 7:7
    (tmin_psp, tmax_psp), (tmin_wind, tmax_wind) = get_timerange(enc)
    legend = (; position=Top())
    labels = '1':'9'
    padding = (0, 30, 0, -30)
    f = Figure(; size=(1000, 800))
    fname = "overview-$enc"
    if add_vl_ratio
        fname = "overview-vl-$enc"
        faxs = plot_PSP(f[1, 1], tmin_psp, tmax_psp, get_vl_ratio_ts(psp_df)...; legend)
        modify_faxs_base!(faxs)
        faxs = plot_Wind(f[1, 2], tmin_wind, tmax_wind - Day(1), get_vl_ratio_ts(wind_df)...; legend)
        modify_faxs_base!(faxs)
    end

    add_labels!(f[1, 1]; labels, open="(a.", padding)
    add_labels!(f[1, 2]; labels, open="(b.", padding)
    display(f)
    easy_save("overview-$enc-all")

    # tplot(f[1, 3], _tmask! .∘ tvars_themis, tmin_wind, tmax_wind; legend)
    # add_labels!(f[1, 3]; labels, open="(c.")
end
```

@@

```{julia}
psp_df_taus = map([2, 4, 8, 16, 32]) do tau
    psp_conf["tau"] = tau
    df = PSPAnisotropy.produce(psp_conf, psp_conf["timeranges"][1]...)
    @transform! df :tau = tau
    compute_Alfvenicity_params!(df)
end

wind_df_taus = map([2, 4, 8, 16, 32]) do tau
    wind_conf["tau"] = tau
    df = PSPAnisotropy.produce(wind_conf, wind_conf["timeranges"][1]...)
    @transform! df :tau = tau
    compute_Alfvenicity_params!(df)
end
```

@@

```{julia}
f = Figure(; size=(1200, 800))
# let df = psp_df_taus[1], config = psp_conf
begin
    df = @subset(wind_df_taus[1], :index_std .> 4)
    config = wind_conf
    event = filter_low_mva_quality(df)[5, :]
    fax, res_psp = plot_candidate(f[1, 1], event, config, Second(10))
    plot_var_info!(fax, event)
    @info "v_l_ratio" event.V_l_ratio event.V_l_ratio_max
end
f
```

@@

# AoG fix
using LaTeXStrings
import AlgebraOfGraphics: append_unit_string
append_unit_string(s::LaTeXStrings.LaTeXString, u::String) = s
```

### 2025-09-29 notebooks/02_stats.qmd
feat: plotting figures

```{julia}
using Dates
using StatsBase, Statistics
using PSPAnisotropy
import Discontinuity as DC
using Discontinuity: var_mapping, compute_params!, filter_low_mva_quality
using Discontinuity: compute_Alfvenicity_params!, Alfven_velocity
using DimensionalData
using DataFrames, DataFramesMeta
using CairoMakie
using Beforerr: _theme_legend, easy_save
using AlgebraOfGraphics
import AlgebraOfGraphics as AoG
using Unitful
Unitful.preferunits(u"nA", u"km")

# https://github.com/MakieOrg/AlgebraOfGraphics.jl/issues/464
foreach([:log10, :log2, :log]) do f
    @eval import Base: $f
    @eval $f(x::Unitful.Quantity) = $f(ustrip(x))
end
set_Z_theme!()
formats = (:pdf,)
```

@@

@chain df begin
    DC.compute_Alfvenicity_params!()
    DC.compute_params!()
    @transform!(
        :B_n_mva_norm = abs.(:B_n_mva ./ :B_mag),
        :duration = _float64.(ustrip.(:duration .|> u"s"))
    )
    DC.classify!(:B_n_mva_norm)
end

@@

fs = map([:mva]) do 𝐧
    𝒎 = var_mapping(; 𝐧)

@@

    vars = [𝒎.l_log, 𝒎.j_log, 𝒎.l_norm_log, 𝒎.j_norm_log]
    # , 𝒎.bn
    labels = ["Thickness", "Current density", "Normalized thickness", "Normalized current density"]

    plt =
        data(tdf) *
        mapping(vars, layout=AoG.dims(1) => renamer(labels)) *
        # mapping(vars, row=AoG.dims(1) => renamer(labels), col=:type) *
        mapping(color=:id, linestyle=:enc) *
        AoG.density(; datalimits) * visual(Lines)
    draw(plt, axis=(; yscale=log10))
    easy_save("$fname-$𝐧"; formats, force=true)
end
fs[1]
```

@@

```{julia}
let df = dropmissing(df, :duration)
    df.duration = ustrip.(df.duration .|> u"s")
    layer = AoG.density(; datalimits=x -> quantile(x, [0.02, 0.99])) * visual(Lines)
    # layer = AoG.histogram(; datalimits=x -> quantile(x, [0.02, 0.99]), bins = 0:0.3:30) * mapping(col=:id)
    plt = data(df) * mapping(:duration, linestyle=:enc, color=:id) * layer
    plt = plt + mapping(2 .^ (1:4)) * visual(VLines, color=:gray, linestyle=:dash)
    # plt *= (mapping(col=direct("col1")) + mapping(color=:tau, col=direct("col2")))
    # scales(Col=(; legend=false))
    draw(plt, axis=(; yscale=log10))
    easy_save("duration_dist"; formats, force=true)
end
```

@@

```{julia}
let df = dropmissing(df, :duration)
    df.duration = ustrip.(df.duration .|> u"s")
    layer = AoG.density(; datalimits=x -> quantile(x, [0.02, 0.99])) * visual(Lines)
    plt = data(df) * mapping(:duration, linestyle=:enc, color=:id) * layer
    plt *= mapping(layout=:tau)
    draw(plt, axis=(; yscale=log10), facet=(; linkxaxes=:none, linkyaxes=:none))
    easy_save("duration_dist_tau"; formats, force=true)
end
```

@@

@@

    plt = alpha_layer(tdf, 0.618) * visual(Scatter; markersize=6, legend=(; alpha=0.6)) * mapping(color=:id, marker=:id)

    fig = Figure(size=(800, 300))
    axis = (; yscale=log10, xscale=log10)
    v_axis = (; yscale=log10, xscale=log10, limits=((2, 400), (2, 400)))

@@

    spec1 = plt * mapping(𝒎.l, 𝒎.j)
    spec2 = plt * mapping(𝒎.l_norm, 𝒎.j_norm)
    spec3 = plt * mapping(:B_n_mva_norm, :ω)
    spec4 = plt * mapping(:ΔV_ratio, :ΔV_cosθ)

@@

    # pretty_legend!(fig, grid1)
    # add_labels!([ga, gb, gc])
    # easy_save("$fname-$enc-$𝐧"; formats, force=true)
    display(fig)
end
```

@@

    B_n_spec = plt * mapping(:B_n_mva_norm, :ω_in) * vis
    ΔV_spec = plt * mapping(:ΔV_ratio, :ΔV_cosθ) * (vis + AoG.linear() * ΔV_cosθ_map)
    σc_σr_spec = plt * mapping(:σ_c, :σ_r) * (vis + AoG.smooth() * visual(color=:red))

@@

    # pretty_legend!(fig, grid1)
    # add_labels!([ga, gb, gc])
    # easy_save("$fname-$enc-$𝐧"; formats, force=true)
    display(fig)
end
```

@@

tdf = @chain df begin
    dropmissing(vars)
    @rsubset(all(!isnan, (:B_n_mva_norm, :Q_sonnerup, :σ_c)); view=true)
    @transform!(
        :duration = Float64.(:duration),
        :B_n_mva_norm = Float64.(:B_n_mva_norm),
    )
end

@@

Q_group = mapping(group=:Q_sonnerup => >(0), color=:Q_sonnerup => >(0))
A_He_group = mapping(group=:A_He => >(0), color=:A_He => >(0))
line_vis = visual(linewidth=3)

Bn_Q_spec = data(Bn_df) * mapping(:B_n_mva_norm, :Q_sonnerup => abs) * layout * (vis + AoG.linear() * line_vis * mapping(color=:id))
duration_Q_spec = plt * mapping(:duration, :Q_sonnerup) * (vis + AoG.smooth() * Q_group * line_vis)
σc_Q_spec = plt * mapping(:σ_c, :Q_sonnerup) * (vis + AoG.linear() * Q_group * line_vis)
σr_Q_spec = plt * mapping(:σ_r, :Q_sonnerup) * (vis + AoG.linear() * Q_group * line_vis)
A_He_Q_spec = data(A_He_df) * mapping(:A_He, :Q_sonnerup => abs) * layout * (vis + AoG.smooth() * A_He_group * line_vis)
β_Q_spec = data(β_df) * mapping(:log_β, :Q_sonnerup => abs) * layout * (vis + AoG.smooth(; degree=4) * line_vis * mapping(color=:id))

draw!(fig[1, 1], Bn_Q_spec)
draw!(fig[1, 2], duration_Q_spec; axis=(; xscale=log10))
draw!(fig[2, 1], σc_Q_spec)
draw!(fig[2, 2], σr_Q_spec)
draw!(fig[3, 1], A_He_Q_spec)
draw!(fig[3, 2], β_Q_spec)

# add_labels!([ga, gb, gc])
easy_save("Q_sonnerup_joint_dist"; formats, force=true)
display(fig)
```

@@

Interpretation:
1. There is a very weak negative correlation between duration and Alfvénicity - meaning longer events tend to be slightly less Alfvénic
2. The effect size is tiny (correlations ~-0.02 to -0.03) - practically negligible
3. Only Q_sonnerup shows statistical significance due to the large sample size (10,684 events)
4. The large sample size makes even tiny correlations statistically detectable, but they're not practically meaningful

>>>>

```{julia}
using Dates
using StatsBase, Statistics
using PSPAnisotropy
import Discontinuity as DC
using Discontinuity: var_mapping, compute_params!, filter_low_mva_quality
using Discontinuity: compute_Alfvenicity_params!, Alfven_velocity
using DimensionalData
using DataFrames, DataFramesMeta
using CairoMakie
using Beforerr: _theme_legend, easy_save
using AlgebraOfGraphics
import AlgebraOfGraphics as AoG
using LinearAlgebra
using Accessors
using Unitful
Unitful.preferunits(u"nA", u"km")

# https://github.com/MakieOrg/AlgebraOfGraphics.jl/issues/464
foreach([:log10, :log2, :log]) do f
    @eval import Base: $f
    @eval $f(x::Unitful.Quantity) = $f(ustrip(x))
end
set_Z_theme!()
formats = (:pdf,:png)
```

@@

A_lens = @optic _.model.A

@chain df begin
    DC.compute_Alfvenicity_params!()
    DC.compute_params!()
    @transform! @astable begin
        :Δ𝐁 = @. norm(:B_us - :B_ds)
        :Δ𝐁_fit = @. 2 * passmissing(A_lens)(:model) |> abs
        :Δ𝐁_norm = :Δ𝐁 ./ :B_mag
        :Δ𝐁_fit_norm = :Δ𝐁_fit ./ :B_mag
        :B_n_mva_norm = abs.(:B_n_mva ./ :B_mag)
        :duration = _float64.(ustrip.(:duration .|> u"s"))
    end
    DC.classify!(:B_n_mva_norm)
end

@@

fs = map([:mva]) do 𝐧
    figure = (; size=(650, 400))
    𝒎 = var_mapping(; 𝐧)

@@

    vars = [𝒎.l_log, 𝒎.l_norm_log, 𝒎.j_log, 𝒎.j_norm_log, :Δ𝐁 => log10 => L"\text{Log }|Δ𝐁|", :Δ𝐁_norm => log10 => L"\text{Log } |Δ𝐁|/B",]
    labels = ["Thickness", "Normalized thickness", "Current density", "Normalized current density", "|Δ𝐁|", "|Δ𝐁|/B"]
    # append!(vars, [ :Δ𝐁_fit => log10 => "Log Δ𝐁_fit", :Δ𝐁_fit_norm => log10 => "Log Δ𝐁_fit_norm"])
    # append!(labels, ["Δ𝐁_fit", "Δ𝐁_fit_norm"])

    plt =
        data(tdf) *
        mapping(vars, layout=AoG.dims(1) => renamer(labels)) *
        # mapping(vars, row=AoG.dims(1) => renamer(labels), col=:type) *
        mapping(color=:id, linestyle=:enc) *
        AoG.density(; datalimits) * visual(Lines)
    draw(plt, scales(Layout=(; palette=wrapped(cols=4, by_col=true))); axis=(; yscale=log10), figure)
    easy_save("$fname-$𝐧"; formats, force=true)
end
fs[1]
```

@@

```{julia}
let df = dropmissing(df, :duration)
    layer = AoG.density(; datalimits=x -> quantile(x, [0.02, 0.99])) * visual(Lines)
    # layer = AoG.histogram(; datalimits=x -> quantile(x, [0.02, 0.99]), bins = 0:0.3:30) * mapping(col=:id)
    plt = data(df) * mapping(:duration, linestyle=:enc, color=:id) * layer
    plt = plt + mapping(2 .^ (1:4)) * visual(VLines, color=:gray, linestyle=:dash)
    # plt *= (mapping(col=direct("col1")) + mapping(color=:tau, col=direct("col2")))
    # scales(Col=(; legend=false))
    draw(plt, axis=(; yscale=log10))
    easy_save("duration_dist"; formats)
end
```

@@

```{julia}
let df = dropmissing(df, :duration)
    layer = AoG.density(; datalimits=x -> quantile(x, [0.02, 0.99])) * visual(Lines)
    plt = data(df) * mapping(:duration, linestyle=:enc, color=:id) * layer
    plt *= mapping(layout=:tau)
    draw(plt, axis=(; yscale=log10), facet=(; linkxaxes=:none, linkyaxes=:none))
    easy_save("duration_dist_tau"; formats)
end
```

@@

```{julia}
function alpha_layer(df, alpha)
    psp_df = @rsubset(df, :id == "PSP"; view=true)
    thm_df = @rsubset(df, :id == "THEMIS"; view=true)
    wind_df = @rsubset(df, :id == "Wind"; view=true)
    (data(thm_df) + data(wind_df)) * visual(; alpha) + data(psp_df)
end

```

@@

    plt = alpha_layer(tdf, 0.618) * visual(Scatter; markersize=6, legend=(; alpha=0.6)) * mapping(color=:id, marker=:id, layout=:id)

    fig = Figure(size=(800, 400))
    axis = (; yscale=log10, xscale=log10)
    v_axis = (; yscale=log10, xscale=log10, limits=((2, 400), (2, 400)))

@@

    # spec1 = plt * mapping(:Δ𝐁_norm, 𝒎.l_norm) # Not strong correlation
    # spec1 = plt * mapping(:Δ𝐁_norm, 𝒎.j_norm) # Not strong correlation
    spec1 = plt * mapping(𝒎.l, 𝒎.j)
    spec2 = plt * mapping(𝒎.l_norm, 𝒎.j_norm)
    spec3 = plt * mapping(:B_n_mva_norm => L"B_{n}/ B", :ω_in => L"ω_{in}")
    spec4 = plt * mapping(:ΔV_ratio => L"|Δ𝐕| / |Δ𝐕_A|", :ΔV_cosθ => L"\cos \theta")

@@

    # pretty_legend!(fig, grid1)
    # add_labels!([ga, gb, gc])
    easy_save("joint_properties-$𝐧"; formats, force=true)
    display(fig)
end
```

@@

    B_n_spec = plt * mapping(:B_n_mva_norm, :ω_in) * AoG.density(npoints=50)
    ΔV_spec = plt * mapping(:ΔV_ratio, :ΔV_cosθ) * (vis + AoG.linear() * ΔV_cosθ_map)
    σc_σr_spec = plt * mapping(:σ_c, :σ_r) * (vis + AoG.smooth() * visual(color=:red))

@@

    # pretty_legend!(fig, grid1)
    # add_labels!([ga, gb, gc])
    display(fig)
end
```

@@

tdf = @chain df begin
    dropmissing(vars)
    @rsubset(all(!isnan, (:B_n_mva_norm, :Q_sonnerup, :σ_c)); view=true)
    @transform!(:B_n_mva_norm = Float64.(:B_n_mva_norm))
end

fig = Figure(; size=(800, 400))
axis = (;)

# layout = mapping(row=:id, col=:enc)
layout = mapping(col=:id)
plt = data(tdf) * layout
den_vis = AoG.density(npoints=50)

# vis = visual(Scatter; markersize=5)
# line_vis = visual(linewidth=3)
# Q_group = mapping(group=:Q_sonnerup => >(0), color=:Q_sonnerup => >(0))
# (vis + AoG.linear() * Q_group * line_vis)
# (vis + AoG.smooth() * A_He_group * line_vis)

Bn_Q_spec = data(Bn_df) * mapping(:B_n_mva_norm => L"B_n/B", :Q_sonnerup => abs  => L"Q") * layout * den_vis
duration_Q_spec = plt * mapping(:duration => log10, :Q_sonnerup => L"Q") * den_vis
σc_Q_spec = plt * mapping(:σ_c => L"σ_c", :Q_sonnerup => L"Q") * den_vis
σr_Q_spec = plt * mapping(:σ_r => L"σ_r", :Q_sonnerup => L"Q") * den_vis

draw!(fig[1, 1], Bn_Q_spec)
draw!(fig[1, 2], duration_Q_spec)
draw!(fig[2, 1], σc_Q_spec)
draw!(fig[2, 2], σr_Q_spec)

# add_labels!([ga, gb, gc])
easy_save("Q_sonnerup_joint_dist_den"; formats, force=true)
display(fig)
```

@@

Q_group = mapping(group=:Q_sonnerup => >(0), color=:Q_sonnerup => >(0))
A_He_group = mapping(group=:A_He => >(0), color=:A_He => >(0))
den_vis = AoG.density(npoints=50)

A_He_Q_spec = data(A_He_df) * mapping(:A_He => log10, :Q_sonnerup => abs) * layout * AoG.density(; npoints=50, datalimits=((-1, 1), (0, 1)))
β_Q_spec = data(β_df) * mapping(:log_β, :Q_sonnerup => abs) * layout * AoG.histogram(; bins=50, datalimits=((-1, 1), (0, 1)))

# draw!(fig[1, 1], Bn_Q_spec)
draw!(fig[3, 1], A_He_Q_spec)
draw!(fig[3, 2], β_Q_spec)

# add_labels!([ga, gb, gc])
# easy_save("Q_sonnerup_joint_dist"; formats, force=true)
display(fig)
```

@@

Interpretation:
1. There is a very weak negative correlation between duration and Alfvénicity - meaning longer events tend to be slightly less Alfvénic
2. The effect size is tiny (correlations ~-0.02 to -0.03) - practically negligible
